\section*{Executive Summary}
\label{s:exec_summ}
%1-page summary with advice for problem owner; what advice do you give the problem owner and why? This advice should be understandable for a general audience unfamiliar with deep uncertainty methods and techniques.
% Convincing advice in light of multi actor context, understandable for non-experts
\begin{multicols}{2}

\noindent Located on the banks of the IJssel River - a river with a history of flooding - a plan for flood risk management is crucial to Gorssel. When coming up with a plan to mitigate these dangers, multiple stakeholders have to be considered. These stakeholders make up a complex actor arena with different objectives, which results in conflict and no one preferred outcome. Paired with the uncertainties and the decision making processes on a local and provincial level, many uncertainties are involved when deciding on a strategy. Therefore, all decisions have to made under deep uncertainty. 

\noindent In this report, we propose a policy strategy for Gorssel during the negotiations for flood risk mitigation in the Province of Overijssel. The research questions answered is \vspace*{\fill} 
\begin{quote} 
\centering 
\textit{How can Gorssel (Dike Ring 4) affordably protect its citizens and businesses from flood risk to a similar level as neighbouring urban areas, while still preserving and protecting farmland from encroachment?}
\end{quote}
\vspace*{\fill}
To accurately assess the effectiveness of Gorssel's policy choices, the possible policy support for other Deventer and Overijssel will also be considered to increase feasibility. 

\bigskip

\noindent There are three ways Gorssel can minimise flood risk: Firstly, Gorssel and Deventer can heighten their dikes; secondly, Overijssel can utilise the Early Warning System as a flood warning system; and lastly, Gorssel and Deventer can implement Room for the River projects. When considering these options, Gorssel wants to minimise land encroachment to protect their farmers' livelihood while ensuring "fairness" in the measures taken across the entire IJssel river. Furthermore, there are three key performance indicators (KPIs) for Gorssel to consider while looking for a suitable strategy. The KPIs consist of expected damage, expected deaths, and the relevant actor's implemented strategy's total cost. We use Exploratory Modelling Analysis (EMA) with the associated workbench to deal with multiple objectives and deep uncertainty. EMA enables the modeller to understand the relation between uncertainties and policies better, resulting in a robust outcome. To start, we identified uncertainties followed by scenario discovery, where we identified possible futures. With this, we could analyse the effectiveness of policies and then or robustness, after which we can make a recommendation. 

\bigskip

% Results 
Robustness and uncertainty analysis from the perspective of Gorssel, Deventer and Overijssel revealed a selection of preferred policies for each actor:
\begin{itemize}
    \item Gorssel: Preferences policies with extensive investment in Room for the River projects and dike heightening in Deventer only, with no or modest dike heightening in Gorssel and earlier warnings for evacuation.
    \item Deventer: Preferences policies with extensive investment in Room for the River projects in Gorssel, accompanied by either significant dike heightening in Gorssel or earlier warnings for evacuation.
    \item Overijssel: Supports low-moderate dike increases in both Gorssel and Deventer, with no investment in Room for the River projects, alongside earlier warnings for evacuations.
\end{itemize}


% Advice 
Based on these results, we recommend that the Municipality of Gorssel consider the following steps for flood risk mitigation:
\begin{enumerate}
    \item Modest dike increases in both Gorssel and Deventer in the near future present a robust solution to minimise flood risk in Gorssel.
    \item Gorssel should support the Overijssel regional government in lobbying for an increase of the Early Warning System to 3 days.
    \item The current scoping of the problem suggests that Room for the River projects are not favourable due to relative costs (compared to dike increases). However, the sensitivity of proposed policies to uncertainty in the probability of a dike failure suggests that these options may warrant further exploration as a policy option.
    \item We recommend that if Gorssel pursues dike heightening projects and EWS increases, that they complement these policies with other activities to improve their real-world robustness.
\end{enumerate}

\noindent At the end of this document, we also include a political reflection, which considers how these recommendations feed into the real-world decision-making environment. The reflection assesses potential challenges to implementing the suggested policies and proposes possible solutions and their impacts.



\end{multicols}