\section{Discussion}
\label{s:discussion}
%Discussion; 

%what are key threats to validity of your conclusions? 
%Robustness metrics? McPhail paper

%What directions do you see for further refining or improving your analysis? Again, this should be grounded in literature and/or an awareness of the decision arena.

% Identifies key limitations of their analysis from both a methodological point of view and the policy arena point of view. Discusses their implications for conclusions and suggests ideas for future work to overcome them
In this section, we look to identify the methodological and policy limitations of our analysis and policy advice and discuss solutions for future work that might help resolve them.

\subsection{Methodological Limitations}
In the analysis process, we made several methodological decisions to enable the effective modelling of the problem posed by Gorssel. While we have justified the critical in Section\ref{s:approach}, a few methodological threats to the validity of this report's policy advice remain.

\subsubsection{Level of Aggregation in the Model}
In choosing the problem formulations for Gorssel, Deventer, and Overijssel, several key variables in the model were either aggregated or disaggregated to achieve a problem formulation that adequately articulated the actor's objectives. Indeed, there is a trade-off between higher levels of aggregation, which may allow for more information to be embedded within fewer objectives, and lower levels of aggregation, which introduces more bias into the problem formulation. For example, \citeauthor{kasprzyk_battling_2016} (\citeyear{kasprzyk_battling_2016}) explain that aggregated, lower objective approaches to modelling might bias decision support tools. However, due to limitations in computation and explainability for clients, some of the objectives had to be aggregated in our modelling approach (for example, Overijssel's problem formulation had an objective of combined deaths for Deventer and Gorssel, rather than optimising them separately).

The aggregation of outcomes overall planning steps also limits the type of policy advice we could provide. By aggregating these outcomes, we are unable to consider the timing of decisions in our policy analysis, limiting our ability to consider reversibility and timeliness of decisions necessary for presenting advice in the form of Dynamic Adaptive Policy Pathways \parencite{kwakkel_coping_2016, marchau_decision_2019}.

It is also feasible that this aggregation created bias related to the influence of different uncertainties. Uncertainty analysis revealed that many of the uncertainties had little to no impact on the outcomes for the actors considered, with Probability of Failure of the Gorssel dike being the most influential factor for the outcomes in the Gorssel analysis.

\textcolor{red}{Conceptual aggregation - Balance between complexity and simplicity in the model - e.g. the model doesn't include climate change, international actors, or broader system scoping - changing the scoping will allow for exploration of whether these conclusions remain valid}

\subsubsection{Validation with Stakeholders}
We did not validate the assumptions applied in the development of problem formulations with input from the client (Gorssel) or the 'rival' stakeholders. Unfortunately, this meant that it wasn't possible to sanity-check the proposed policies or revise the problem formulations in light of expert input. As a result, only one iteration was performed over the complete Multi-Scenario MORDM process to generate the policy advice presented in Section \ref{s:results}. This may limit the relevancy and robustness of the proposed policies, as well as the likelihood of acceptance by stakeholders \parencite{quinn_rival_2017}.

Further to this, we made assumptions about the objectives and constraints for stakeholders, which influenced how the problem formulations structures. For example, in its problem formulation, Deventer has a hard constraint on dike increases. This generated some unusual policies, which warrants further investigation.

\subsubsection{Limited Use of Uncertainty Analysis and Scenario Discovery}
The uncertainty analysis and scenario discovery results from the preliminary round of MORDM were not employed effectively in the subsequent selection of scenarios. Time constraints in the analysis process meant that we did not adequately incorporate information on uncertainties to adjust the uncertainty ranges over which we sampled selected scenarios. We could have better incorporated the results from these analyses into decreasing the dimensionality and uncertainty of the selected scenarios, which could have reduced the computational intensity of other downstream tasks in the multi-scenario MORDM. This limitation may also explain why the final proposed policies remain highly sensitive to a single input factor (probability of dike failure at Gorssel).

\subsubsection{Inefficient Order of Steps}
As can be seen in Figure~\ref{fig:msmordm} in Section \ref{s:approach}, we selected our subset of policies after we had re-evaluated under deep uncertainty. This wasted computational power on re-evaluating policies that we excluded by the next step. This is very unfortunate, as 1000 scenarios per policy is relatively small.

\subsubsection{Limitations of RDM}
RDM is a strong approach for handling wicked problems but is not without its own limitations \parencite{kwakkel_coping_2016}. For example, RDM enabled us to investigate the trade-offs of different policies, but this method is limited in its adaptability once implemented. Further to this, anecdotal evidence suggests that Rijkswaterstaat advocates adaptive planning, and policy proposals, even at the municipal level, should look to come in line with national approaches.

\subsubsection{Creation of the 'Difference' Objectives}
In translating Gorssel's mandate from problem framing into model problem formulation, we initially looked at minimising the difference between damage in Gorssel and Deventer. We proposed this as a means of quantifying the 'fairness' of different policies in terms of effects in rural and urban areas. However, after further consideration, we decided that minimising this as an objective was arguably too Machiavellian, given that minimising this to below zero is effectively choosing scenarios that maximise deaths in Deventer, often without any additional benefit to Gorssel.

Instead, we retained this objective to calculate sensitivities to capture the intangible concepts of fairness and equality between urban and rural areas. However, this decision meant that the objective is more for Gorssel's benefit and does not add any analytical rigour to the definition of 'fairness'. Further to this, the difference value in optimisations is always favouring Gorssel, but it remains uncertain that this covers the fundamental inequity between the rural and urban actors. For example, Gorssel probably receives a lot less revenue, so damages there are probably more impactful than in Deventer.


\subsection{Policy Arena Limitations}

The policy arena was demarcated in section \ref{s:prob_frame}. However, the manner thereof may leave some blind spots and create limitations that further analysis should address. We will address these concerns in the following subsections.  

\subsubsection{Model Scope versus Real World}
To reiterate, the manner of scoping is that we have merely looked at decision making within the province of Overijssel. This means that our analysis fails to consider the implementations of upstream dike rings. However, in reality, the implementation of upstream strategies have the power to render our found policies ineffective. 
\textcolor{red}{(EXAMPLE?)}

Besides this, particularly within our defined scope, financial aspects significantly impact the choices each actor makes. This has to do with the "fairness" we seek for Gorssel, and others also seek this same "fairness" for their own dike ring. For instance, Dike Rings 1 to 3, located upstream, care about the funds being made available for Dike Ring 4 and 5, as this means there will be fewer funds available for the projects in their area. 

Lastly, our regional scoping means we did not infer the complete consequences of an Early Warning System. The model consists of actors across Dutch provinces. The EWS is a "global" policy - meaning that it would affect all RfR actors and not merely the one within the scope. All actors, or critical mass, would need to be convinced instead of just those within the scope. Future model iterations could include more agents to confirm whether this global policy is desirable or not.


\subsubsection{Decision Making Processes}
The current scoping of the policy solutions may conflict with Rijkswaterstaat's actual manner of top-down planning. Conflicts between bottom-up and top-down planning and implementation of policies may create inefficiencies or results in missed opportunities \parencite{koontz_planning_2014}. For Gorssel, the focus of objectives was concerned with preparing a strategy on how to develop a proposal with the province of Overijssel. This means that while the analysis is relevant in this context, it may fail to account for the reality of how Rijkswaterstaat functions. Similarly, it may not always be possible to implement the decisions made in the model in reality. For instance, if the region invests first in dike strengthening and Room for the River follows after, the dikes would have to be altered or dismantled. 

\subsubsection{Dependency on Models}
To better serve Gorssel, the base model given by Rijkswaterstaat was adjusted, such as the disaggregation of costs of Room for the River projects. This was done to suit Gorssel better but poses a problem when other actors in the policy arena use the same (base) model or have also made small adjustments, as we may not be able to assume a consensus exists among all actors, as \citeauthor{kwakkel_coping_2016} (\citeyear{kwakkel_coping_2016}) writes is important to have. Our client should treat this advice with a certain wariness, so they're not used to support actors' agendas. Models are frequently misused to support agendas \parencite{saltelli_five_2020}. A way to prevent this negotiated nonsense is validation through stakeholders and experts. 

\subsection{Proposed Improvements and Further Work}
Proposed solutions for each of these limitations are considered in light of current knowledge and available literature. These improvements are summarised in Table \ref{tab:Proposed Solutions}.

\begin{table}[h]
\caption{Proposed solutions for each of the identified limitations}
\label{tab:Proposed Solutions}
\centering
\begin{tabular}{p{0.2\textwidth}|p{0.7\textwidth}}
\textbf{Limitation} & \textbf{Proposed Solution}  \\ \hline
Levels of aggregation & Future work should look to disaggregate factors (especially cost objectives) to identify whether the aggregation of these factors introduced bias in the policy analysis favouring one approach or another. \\ \hline
Inefficient order of analysis &  It is more efficient first to select a subset of policies, then re-evaluate under deep uncertainty.\\ \hline
Limitations of RDM and reversibility of decisions & Re-evaluate the problem for multiple time steps and consider applying dynamic adaptive policy pathways (DAPP). The selection of the style of proposed policy should ultimately match the client's risk tolerance and preferences regarding adaptive planning \parencite{marchau_decision_2019}. \\ \hline
Lack of validation with stakeholders &Analysts should conduct additional iterations on the model specification and frame in light of identified policies and scenarios. Having identified opportunities for coalitions (or tensions between policies of different actors), should iterate through the Multi-scenario MORDM process again following consultation with the client and stakeholders, re-specifying the problem formulations, or adding in new issues or objectives. For instance, running new problem formulations for actors in Gelderland province to test the policies against their objectives and preferences. \\ \hline
Limited application of uncertainty analysis and scenario discovery & Further iterations on the multi-scenario MORDM should better incorporate insights from the uncertainty analysis, such that a more specific set of scenarios are selected for the analysis and optimisation of the policies \parencite{watson_incorporating_2017, eker_including_2018}. \\ \hline
Creation of difference objectives & Investigate alternative robustness metrics through consultation with stakeholders and client. There are a range of metrics that could serve to underline robustness in terms of inequities in proposed policies \parencite{mcphail_robustness_2018}. \\ \hline
Scoping of the model relative to reality & Additional iterations at various scopes of the problem with the recommended policies may work well to show how the chosen policy would function under different scopes.        \\ \hline
Decision-making processes & A way to counter this would be to perhaps find a manner to be more involved in the final decision-making process at provincial level   \\ \hline
Dependency on models &  Better communication between analysts and modellers would allow for aligning the different models and perhaps allow for an understanding of differences. Furthermore, transparency and naming the vulnerabilities of the models used can build trust \parencite{saltelli_five_2020}.               
\end{tabular}
\end{table}